%Appendix A
\chapter*{\textbf{APPENDIX A}} \label{APPENDIX A}

\begin{center}
	\textbf{Research publications}\\
	\vspace{0.5cm}
\end{center}

\noindent
Below are lists of contributions in form of publications and presentations: \\

\noindent
Book series
\begin{itemize}
	\item M.R. Othman, J.U. Repke \& G. Wozny. 2010. "Incorporating Negative Values in AHP Using Rule-Based Scoring Methodology for Ranking of Sustainable Chemical Process Design Options". Computer Aided Chemical Engineering. Vol. 28, pp. 1045-1050A.
\end{itemize}

\noindent
Journal publication
\begin{itemize}
	\item M.R. Othman, J.U. Repke, G. Wozny \& Y. Huang. 2011. "Sustainability Assessment \& Decision Making for Sustainable Chemical Process Option". To be appear in Chinese Journal of Chemical Engineering.
	\item M.R. Othman, J.U. Repke, G. Wozny \& Y. Huang. 2010. "A Modular Approach to Sustainability Assessment and Decision Support for Chemical Process Design".  Industrial \& Engineering Chemistry Research. 49 (17), pp. 7870-7881.
\end{itemize}


%Appendix B
%insert here if you have several appendix
\chapter*{\textbf{APPENDIX B}} \label{APPENDIX B}

\begin{center}
	\textbf{Conference presentations}\\
	\vspace{0.5cm}
\end{center}

\noindent
Conference presentation 
\begin{itemize}
\item M.R. Othman, L. Hady, J.U. Repke \& G. Wozny. 2011. "Introducing Decision Making Methodology into Chemical Engineering Education". 8th European Congress of Chemical Engineering. 25-29 September 2011. Berlin, Germany. POSTER

\item M.R. Othman, J.U. Repke \& G. Wozny. 2011. "Selection of Sustainable Chemical Process Design using ANP: A Biodiesel Case Study". International Symposium on the Analytic Hierarchy Process (ISAHP). 15-18 June 2011. Sorrento, Naples, Italy. ORAL

\item M.R. Othman, J.U. Repke \& G. Wozny. 2010. "Incorporating Negative Values in AHP Using Rule-Based Scoring Methodology for Ranking of Sustainable Chemical Process Design Options". 20th European Symposium on Computer Aided Process Engineering (ESCAPE 20). 6-9 June 2010. Ischia, Naples, Italy. ORAL

\item M.R. Othman, J.U. Repke, G. Wozny \& Y. Huang. 2010. "Sustainability Assessment and Decision Making for Sustainable Chemical Process Option". 2nd International Symposium on Sustainable Chemical Product \& Process Engineering (ISSCPPE2). 9-12 May 2010. Hangzhou, China. ORAL \& POSTER

\item M.R. Othman, J.U. Repke, G. Wozny \& Y. Huang. 2009. "A Modular Approach to Sustainability Assessment \& Decision Support in Chemical Process Design". AIChE: 1st International Congress on Sustainability Science \& Engineering (ICOSSE). 10-13 August 2009. Cincinnati, Ohio, USA. ORAL
\end{itemize}

